Figures for conference paper

### 2019-04-24 conference figures.Rmd
flow chart

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)

@@

>>>>

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)
library(DiagrammeR)

@@

# Flow chart

```{r}
test <- grViz("digraph flowchart {

      node [fontname = Helvetica, shape = rectangle]

      # Input Data
      subgraph cluster0 {
      label = 'Input Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      # User Input
      subgraph cluster1 {
      label = 'User Input';
      style = filled;
		  color = coral;
		  node [style = filled, color = black, fillcolor = white];
      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      # Ouput
      subgraph cluster2 {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings \n and Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      TE [label = 'Student큦 Topic Expertise']
      AI [label = 'Student큦 Academic Interests']
      AP [label = 'Student큦 Academic Performance']
      PM [label = 'Predictive Models']
      GP [label = 'Grade Prediction']
      TR [label = 'Student큦 Transcript']

      # edges
      {TE, KW} -> AI; 
      {ID, SD} -> TR;
      TR -> AP;
      {TR, TM} -> TE;
      {PM, TE, AP, CS} -> GP;
      GP -> WAR;

      edge[label = 'LDA']
      CD -> TM;

      edge[label = 'Lasso']
      SD -> PM;

      edge[label = 'KL distance']
      {TM, AI} -> SUG
      }
      ")

# Save by hand
# image format: JPEG
# Width: 626
# Check Maintain aspect ratio
# File name: Conference/Figures/Flowchart
```
